Map/Reduce for the common man

### 2010-02-19 doc/slides.tex
*** empty log message ***

\begin{frame}\frametitle{Special Case}
  \emph{idea}: fold as early as possible, as in
  \begin{displaymath}
    \sum_{x\in l}f(x) = \mathtt{map\_fold}~f~(+)~0~l
  \end{displaymath}
  in this case, + is \emph{associative / commutative}, so reductions are
  order-insensitive and can be performed as soon as two intermediate
  results are available

@@

\begin{frame}\frametitle{Local/Remote reductions}
  reductions can be performed either by the master (local) or by the
  workers (remote)

  \bigskip
  remote reductions allow other computations to be performed in parallel

@@

    \newcommand{\Lo}{\colorbox{orange}{~~}\,}
    \renewcommand{\Re}{\colorbox{red}{~~}\,}
    \newcommand{\Se}{\colorbox{blue}{~~}\,}
    \newcommand{\Pa}{\colorbox{kwblue}{~~}\,}

@@

  \begin{itemize}
  \item a worker starts a server, waiting for tasks
  \item the master connects to workers, sending tasks
  \end{itemize}

  simple, string-based protocol:
  \begin{center}
    \begin{tabular}{ccc}
      \framebox{master} &  & \framebox{worker} \\
      &     $\stackrel{\displaystyle connect}{\longrightarrow}$ &  \\
      &     $\stackrel{\displaystyle\mathtt{Assign}~3~\mathtt{"f"}~\mathtt{"7"}}
                      {\longrightarrow}$ &  \\
      &     $\stackrel{\displaystyle \mathtt{Started}~3}
                      {\longleftarrow}$ &  \\
      &     $\stackrel{\displaystyle 
                       \only<1>{\mathtt{Completed}~3~\mathtt{"42"}}
                       \only<2>{\emph{\mathtt{Aborted}~3~}}
                       \only<3>{\emph{\mathtt{Kill}~3}}}
                      {\only<1-2>{\longleftarrow}
                       \only<3>{\longrightarrow}}$ &  \\
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Network: Polymorphic Map/Reduce}
  if master and workers are \emph{exactly} the same executable, then
  marshalling can still be used to pass values $\Rightarrow$
  polymorphic map/reduce

>>>>

\begin{frame}\frametitle{Local/Remote folds}
  folds can be performed either by the master (local) or by the
  workers (remote)

  \bigskip
  remote folds allow other computations to be performed in parallel

\begin{frame}\frametitle{Special Case}
  \emph{idea}: fold as early as possible, as in
  \begin{displaymath}
    \sum_{x\in l}f(x) = \mathtt{map\_fold}~f~(+)~0~l
  \end{displaymath}
  in this case, + is \emph{associative / commutative}, so folds are
  order-insensitive and can be performed as soon as two intermediate
  results are available

@@

@@

    \newcommand{\Lo}{\colorbox{orange}{~\textcolor{white}{\small L}~}\,}
    \renewcommand{\Re}{\colorbox{red}{~\textcolor{white}{\small R}~}\,}
    \newcommand{\Se}{\colorbox{blue}{~\textcolor{white}{\small S}~}\,}
    \newcommand{\Pa}{\colorbox{kwblue}{~\textcolor{white}{\small P}~}\,}

@@

  \begin{itemize}
  \item a worker starts a server, waiting for tasks
  \item the master connects to workers, sending tasks
  \item when done, the master sends result to the workers
  \end{itemize}

  simple, string-based protocol:
  \begin{center}
    \begin{tabular}{ccc}
      \framebox{master} &  & \framebox{worker} \\
      &     $\stackrel{\displaystyle connect}{\longrightarrow}$ &  \\
      &     \pause $\stackrel{\displaystyle\mathtt{Assign}~3~\mathtt{"f"}~\mathtt{"7"}}
                      {\longrightarrow}$ &  \\
      &     \pause $\stackrel{\displaystyle \mathtt{Started}~3}
                      {\longleftarrow}$ &  \\
      &     \pause $\stackrel{\displaystyle 
                       \only<4>{\mathtt{Completed}~3~\mathtt{"42"}}
                       \only<5>{\mathtt{Result}~\mathtt{"89"}~}
                       \only<6>{\emph{\mathtt{Aborted}~3~}}
                       \only<7>{\emph{\mathtt{Kill}~3}}
                      }
                      {\only<4,6>{\longleftarrow}
                       \only<5,7>{\longrightarrow}}$ &  \\
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Network: Polymorphic Map/Reduce}
  if master and workers are compiled from the \emph{same source} using the
  \emph{same Ocaml version}, then
  marshalling can still be used to pass values $\Rightarrow$
  polymorphic map/reduce
